%-------------------------
% Resume in Latex
% Author : Peter Gunarso
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Peter Gunarso} \\ \vspace{1pt}
    16254 Ne 2nd St, Bellevue WA 98008 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 425-442-9443 ~ \href{mailto:peter@gunar.so}{\raisebox{-0.2\height}\faEnvelope\  \underline{peter@gunar.so}} ~
    \href{https://www.linkedin.com/in/pgunarso/}{\raisebox{-0.2\height}\faLinkedin\ \underline{www.linkedin.com/in/pgunarso/}}  ~
    \href{https://github.com/gunarp}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/gunarp}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Sep. 2018 -- Dec. 2021}
      {Bachelor of Science in Computer Engineering, GPA: 3.71}{Seattle, WA}
    \resumeSubSubheading
      {Minor in Applied Mathematics}{}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Algorithms
                \item Database Management
                \item Distributed Systems
                \item Operating Systems
                \item Networks
                \item Machine Learning
                \item Digital Design
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Underwater Remotely Operated Vehicles (UWROV)}{Jan 2019 -- November 2021}
    {Software Lead}{Seattle, WA}
    \resumeItemListStart
      \resumeItem{Led team of 11 students to design, test, and document software components
                  of an ROV which competed in the 2021 international MATE ROV competition.}
      \resumeItem{Implemented subroutines to enable ROV to interact with the physical
                  world using motors, sensors, and manipulators.}
      \resumeItem{Designed training materials for new members to learn basics of ROS,
                  circuitry, and computer vision.}
      \resumeItem{Assisted in managing club organization, finances, and scheduling.}
    \resumeItemListEnd

    \resumeSubheading
      {Nordstrom Tech}{June 2021 -- August 2021}
      {Software Engineer Intern}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Supported the enterprise authentication team which enables 70k+ employees
                    and external vendors to securley and conveniently access Nordstrom applications and resources.}
        \resumeItem{Created a set of dashboards which visualize key authentication data using JavaScript, Python, and Splunk.}
        \resumeItem{Created and deployed a CronJob which automatically suspends inactive users using Java, Docker, and Kubernetes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{MATE ROV 2021 Machine Learning Challenge} $|$
              \emph{Azure, Python, JavaScript}}{April 2021 - June 2021}
        \resumeItemListStart
          \resumeItem{Led team of 4 to create series of computer vision algorithms to recognize,
                      categorize, and record sightings of fish in a given video.}
          \resumeItem{Created an Electron app which submitted a video to an Azure-hosted server
                      and displayed the results of the algorithm.}
          \resumeItem{Placed 3rd internationally in the MATE ROV 2021 Machine Learning Challenge.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{ImPosture} $|$ \emph{JavaScript, React, PoseNet}}{October 2020}
          \resumeItemListStart
            \resumeItem{Created a free, React based app meant to help users improve their posture
                        while sitting at their desk during quarantine.}
            \resumeItem{Used the TensorFlow JavaScript PoseNet model, which used a camera
                        stream to determine a user's pose entirely through the user's web browser.}
            \resumeItem{Used React and Node.js to build core functionality in both front and back ends.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\emph{League of Legends} Ranked Data Gathering and Analysis Project} $|$ \emph{Python, Pandas, AWS}}{June 2019}
          \resumeItemListStart
            \resumeItem{Created Python script to collect, store, analyze, and visualize hundreds
                        of gigabytes of ranked play data from \emph{League of Legends} Ranked Data API.}
            \resumeItem{Used AWS to continously gather and store data using Python script for two weeks.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, JavaScript, SQL, \LaTeX} \\
     \textbf{Developer Tools}{: VS Code, IntelliJ, AWS, Docker, Kubernetes, Git, JUnit} \\
     \textbf{Technologies/Frameworks}{: Pandas, Numpy, Unix, OpenCV, ROS, FreeRTOS} \\
     \textbf{Skills}{: Algorithm Design, System Design, Computer Vision, Data Analysis, Leadership, Verbal and Written Communication}\\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Mana Group LLC}{2016 -- Present}{Shipping Consultant}{}
            \resumeItemListStart
                \resumeItem{Communicated with dozens of clients every week in a retail setting. Workedto pinpoint their shipping needs, suggested appropriate options which balancedprice, speed, and safety.}
                \resumeItem{Used Flask to develop a web app to compare shipping rates across 3 carriersand 10 services.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd


\end{document}